---
title: 'NYC Restaurant Inspections'
date: "May 2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction  
NYC Restaurant Inspections Intro  
  
 
## Preparation   
The following R libraries will be used: 
  - library(dplyr)
  - library(tibble)
  - library(stringr)
  - library(tidyverse)
  - library(tidyr) 
  - library(purrr) 
  - library(RSocrata)
  - library(ggplot2) 
  - library(lubridate)
  - library(tm) 
  - library(SnowballC) 
  - library(wordcloud) 
  - library(RColorBrewer) 
  

## Dataset 
  Describe dataset  
  

```{r}
library(dplyr)
library(tibble)
library(stringr)
library(tidyverse)
library(tidyr) 
library(purrr) 
library(RSocrata)
library(ggplot2) 
library(lubridate)
library(tm) 
library(SnowballC) 
library(wordcloud) 
library(RColorBrewer)
library(utils)

```

```{r}

# Import the data and look at the first six rows
df <- read.csv("~/Desktop/DSC 680/Week12/DOHMH_New_York_City_Restaurant_Inspection_Results.csv")
head(df)

```

```{r}

# Converts the Date fields from POSIXlt to date
date_conv <- function(x){
    if (identical(unlist(class(x))[1],"POSIXlt")){
        x<-as.Date(x)
    } else(x)
}

##  created a tible from data frame
df_tib <- as_tibble(map(df,date_conv))

head(df_tib[1:20,])

```

```{r}

#Inspections results for 2020
inspections = unique(select(df_tib, CAMIS, BORO, ZIPCODE, CUISINE.DESCRIPTION, INSPECTION.DATE, INSPECTION.YEAR, ACTION, SCORE, GRADE)) 
inspections = filter(inspections, INSPECTION.YEAR == '2020' & (GRADE == 'A'| GRADE== 'B'| GRADE== 'C') & ACTION !='closed' & BORO !='Missing')

# Selects only the latest for each restaurant
latest = merge( aggregate(INSPECTION.DATE ~ CAMIS, inspections, max), inspections) #Unique restaurants and their latest score/grade 

# List of unique restaurants and their grade for 2020
restaurants = unique(select(latest, CAMIS, BORO, ZIPCODE, CUISINE.DESCRIPTION, SCORE, GRADE))

```

```{r}

ggplot(data=restaurants, aes(x=reorder(BORO, desc(BORO)))) + 
    geom_bar(aes(fill=GRADE), position='dodge') + 
    labs(title='Grades in each NY Borough for 2020', x='Borough', y='# of Restaurants') + scale_y_continuous(limits=c(0,2300), breaks=seq(0,10000,1000)) + 
    theme_bw()

```

```{r}
library(dplyr)
# text mining library
library(tidytext)
library(igraph)
library(ggraph)

textdata<- df_tib%>%
        filter(INSPECTION.YEAR == 2020 & (GRADE =='A'| GRADE=='B'| GRADE=='C') & ACTION !='closed' & BORO !='Missing')%>%
        select(VIOLATION.DESCRIPTION)

textdata$StrippedText <- gsub("&amp","", textdata$VIOLATION.DESCRIPTION)

nyc_clean <- textdata %>%
  dplyr::select(StrippedText) %>%
  unnest_tokens(word, StrippedText)



# plot the top 15 words -- notice any issues?
nyc_clean %>%
  count(word, sort = TRUE) %>%
  top_n(15) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(x = "Count",
       y = "Unique words",
       title = "Count of unique words found in NYC Violation Descriptions")


```

```{r}

# load list of stop words - from the tidytext package
data("stop_words")
# view first 6 words
head(stop_words)

nrow(nyc_clean)

# remove stop words from your list of words
cleaned_nyc_words <- nyc_clean %>%
  anti_join(stop_words)

nrow(cleaned_nyc_words)

cleaned_nyc_words

# plot the top 15 words -- notice any issues?
cleaned_nyc_words %>%
  count(word, sort = TRUE) %>%
  top_n(15) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in NYC Violation Descriptions",
       subtitle = "Stop words removed from the list")


```

```{r}
library(widyr)

# remove punctuation, convert to lowercase, add id for each tweet!
nyc_paired_words <- textdata %>%
  dplyr::select(StrippedText) %>%
  unnest_tokens(paired_words, StrippedText, token = "ngrams", n = 2)

nyc_paired_words %>%
  count(paired_words, sort = TRUE)

library(tidyr)
nyc_separated_words <- nyc_paired_words %>%
  separate(paired_words, c("word1", "word2"), sep = " ")

nyc_filtered <- nyc_separated_words %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

nyc_filtered

# new bigram counts:
nyc_words_counts <- nyc_filtered %>%
  count(word1, word2, sort = TRUE)

head(nyc_words_counts)

```

```{r}
set.seed(1234)
wordcloud(words = nyc_words_counts$word1, freq = nyc_words_counts$n, min.freq = 200,
        max.words=70, random.order=FALSE, rot.per=0.5, 
        colors=brewer.pal(8, "Dark2")
        )


```

```{r}

top_restaurant <- function(df12,x,y){
    dt<-df12%>%
    filter(INSPECTION.YEAR == x)%>%
    filter(str_detect(VIOLATION.DESCRIPTION, regex("y", ignore_case = TRUE)))%>%
    group_by(CAMIS,DBA)%>%
    summarise(count=n())%>%
    arrange(desc(count))%>%
    head(10)
    print(dt)

}

# function call
top_restaurant(df_tib,2020,"contamination")

```




#

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
